Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-08 paper/paper.tex
Creat non-floating tables for metrics in report

% TODO: Table of positional offset statistics
% TODO: Table of completeness statistics
% TODO: Statement on completeness

@@

\begin{table}[]
\begin{tabular}{lllll}
    & Total number of buildings & Area cover & Number of buildings (\%) & Area cover (\%) \\
    OSM & 102755 & 33105023.32... $m^2$ & 60.17\% & 98.18\% \\
    SLU & 170783 & 33718628.97... $m^2$ & 100.00\% & 100.00\%
\end{tabular}
\end{table}

@@

\begin{table}[]
\begin{tabular}{lllll}
    & 1:0 & 1:1 & 1:n & Total \\
    Match count & 9812 & 81722 & 11221 & 102755
\end{tabular}
\end{table}

>>>>

@@

\begin{table}[H]
\begin{tabular}{lllll}
    & Total number of buildings & Area cover \\
    OSM & 102755 & 33105023.32... $m^2$ \\
    SLU & 170783 & 33718628.97... $m^2$
\end{tabular}
\end{table}

\begin{table}[H]
\begin{tabular}{lllll}
    & Number of buildings (\%) & Area cover (\%) \\
    OSM & 60.17\% & 98.18\% \\
    SLU & 100.00\% & 100.00\%
\end{tabular}
\end{table}

@@

\begin{table}[H]
\begin{tabular}{lllll}
    & 1:0 & 1:1 & 1:n & Total \\
    Match count & 9812 & 81722 & 11221 & 102755
\end{tabular}
\end{table}
